\bf Forecasts Reconciliation: A geometric view with new insights on bias correction.

### 2019-08-22 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Revision 1

	\if1\blind
	{
		\title{\bf Forecasts Reconciliation: A geometric view with new insights on bias correction.}
		\author{Puwasala Gamakumara\thanks{
				The authors gratefully acknowledge the support of Australian Research Council Grant DP140103220.  We also thank Professor Mervyn Silvapulle for valuable comments.}\hspace{.2cm}\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3800, Australia.\\
			Email: Puwasala.Gamakumara@monash.edu \\
			and \\
			Anastasios Panagiotelis\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3800, Australia.\\
			Email: Anastasios.Panagiotelis@monash.edu \\
			and \\
			George Athanasopoulos\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3800, Australia.\\
			Email: george.athanasopoulos@monash.edu \\
			and \\
			Rob J Hyndman\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3800, Australia.\\
			Email: rob.hyndman@monash.edu \\}
		\maketitle
	} \fi

@@

	Multivariate time series following an aggregation structure arise in many disciplines such as manufacturing, engineering, marketing and medicine\todo{include references}. Forecasts of these series should adhere to aggregation constraints to ensure aligned decision making. Earlier studies achieved this by only forecasting a single level of the hierarchy and then either aggregating in a bottom up fashion \citep{Dunn1976} or disaggregating in a top-down fashion \citep{Gross1990, Athanasopoulos2009}.  For reviews of these approaches including a discussion of their advantages and disadvantages see \citet{Schwarzkopf1988, Kahn1998, Lapide1998, Fliedner2001}.

	In contrast to these methods, \cite{Hyndman2011} proposed forecasting all series in the hierarchy, referring to these as {\em base} forecasts.  Since base forecasts were produced independently they were not guaranteed to adhere to aggregation constraints and could thus be improved via further adjustment.  A framework was proposed whereby the base forecasts were assumed to follow a regression model.  The predicted values from this model were guaranteed to adhere to the linear constraints by construction and could thus be used as a new set of forecasts.  This approach and later modifications have subsequently been shown to outperform bottom up and top down approaches in a variety of empirical settings\todo{references}.

@@

	The remainder of this paper is structured as follows. Section~\ref{sec:CoheForecasts} deals with the concept of coherence and defines so called hierarchical time series in a way that does not depend on any notion of bottom level series.  Section~\ref{sec:Reconciliation} defines forecast reconciliation in terms of projections and includes a proof that reconciled forecasts dominate base forecasts with respect to a specific loss function. In Section~\ref{sec:BiasInRecon} we prove the unbiasedness preserving property of reconciliation via certain projection matrices and propose methods for bias correction. In Section \ref{sec:EmpStudy} we evaluate these methods for in an extensive emprirical application to domestic tourism flow in Australia.  Section~\ref{sec:conclusions} concludes with some discussion and thoughts on the  future of research in forecast reconciliation.  
\section{Coherent forecasts}\label{sec:CoheForecasts}

@@

    We briefly define the concept of a \emph{hierarchical time series} in a fashion similar to \cite{WicEtAl2019}, \cite{FPP2018} and others, before elaborating on some of the limitations of this understanding.  A \emph{hierarchical time series} is a collection of $n$ variables indexed by time, where some variables are aggregates of other variables. We let $\bm{y}_t \in \mathbb{R}^n$ be a vector comprising observations of all variables in the hierarchy at time $t$. The \emph{bottom-level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables; we let $\bm{b}_t \in \mathbb{R}^m$ be a vector comprised of observations of all bottom-level series at time $t$.  The hierarchical structure of the data implies that the following holds for all $t$

@@

     To further illustrate, Figure \ref{fig:3D_hierarchy} depicts the most simple three variable hierarchy where $y_{Tot,t}=y_{A,t}+y_{B,t}$.  The coherent subspace is depicted as a grey $2$-dimensional plane within $3$-dimensional space, i.e. $m=2$ and $n=3$.  It is worth noting that the coherent subspace is spanned by the columns of $\bm{S}$, i.e.\ $\mathfrak{s}=\text{span}(\bm{S})$.  In Figure~\ref{fig:3D_hierarchy}, these columns are $\vec{s}_1=(1,1,0)'$ and $\vec{s}_2=(1,0,1)'$.  However, it is equally important to recognise that the hierarchy could also have been defined in terms of $y_{Tot,t}$ and $y_{A,t}$ rather than the bottom level series, $y_{A,t}$ and $y_{B,t}$. In this case the corresponding `$\bm{S}$ matrix' would have columns $(1,0,1)'$ and $(0,1,-1)'$.  However, while there are multiple ways to define an $\bm{S}$ matrix, in all cases the columns will span the same coherent subspace, which is unique.

     \begin{figure}[H]
     	\centering
     	\vspace{-0.9cm}
     	\small
     	\resizebox{\linewidth}{!}{
     		\input{Figs/3D_hierarchy}
     	}
     	\caption{Depiction of a three dimensional hierarchy with $y_{\text{Tot}} = y_{\text{A}} + y_{\text{B}}$. The gray coloured two dimensional plane depicts the coherent subspace $\mathfrak{s}$ where $\vec{s}_1 = (1,1,0)'$ and $\vec{s}_2 = (1, 0, 1)'$ are basis vectors that spans $\mathfrak{s}$. The red points in $\mathfrak{s}$ represent realisations or coherent forecasts}\label{fig:3D_hierarchy}
     \end{figure}

@@

	 Despite the common use of the term {\em hierarchical time series}, it should be clear from the definition that the data need not necessarily follow a hierarchy.  Also notable by its absence in the above definition is any reference to {\em aggregation}. In some ways, terms such as {\em hierarchical} and {\em aggregation} can be misleading since the literature has covered instances that cannot be depicted in a similar fashion to Figure~\ref{fig:basichier} and/or do not involve aggregation. {\bf Include brief summary of all non-traditional hierarchies - e.g. grouped hierarchies, temporal hierarchies with weird overlapping, problems where we look at differences between variables etc.}  Finally, although Definition~\ref{def:cohspace} makes reference to time series, this definition can be easily generalised to any vector-valued data for which some linear constraints are known to hold for all realisations.

@@

    Without any loss of generality, the above definition could also be applied to prediction for multivariate data in general, rather than just forecasting of time series.  Much of the early literature that dealt with the problem of forecasting hierarchical time series \citep[see][and references therein]{Gross1990} produced forecasts at a single level of the hierarchy in the first stage. Subsequently forecasts for all series were recovered through aggregation, disaggregation according to historical or forecast proportions or some combination of both.  As such incoherent forecasts were not a problem in these earlier papers.

    Forecasting a single level of the hierarchy did not, however echo common practice within many industries.\todo{might need refs}  In many organisations different departments or `silos' each produced their own forecasts, often with their own information sets and judgemental adjustments.  This approach does have several advantages over only forecasting a single level.  First, there is no loss of information since all bottom levels are modelled.  Second, modelling top level series often identifies features such as trend and seasonality that cannot be detected in noisy disaggregate data.  Unfortunately, however, when forecasts are produced independently at all levels, forecasts are likely to be incoherent.  This problem of incoherent forecasts cannot in general be solved by multivariate modelling either.  Instead, the solution to incoherent forecasts is to make an ex post adjustment that ensures coherence, a process known as {\em forecast reconciliation}

@@

	The problem of forecast reconciliation is predicated on there being an $n$-vector of forecasts that are incoherent.  We will call these {\em base forecasts} and denote them as $\hat{\bm{y}}_{t+h|h}$.  In the sequel, this subscript will be dropped at times for ease of exposition.  In the most general terms, reconciliation can be defined as follows

	\begin{definition}[Reconciled forecasts]\label{def:reconpoint}
		Let $\psi$ be a mapping, $\psi:\mathbb{R}^n\rightarrow\mathfrak{s}$.  The point forecast $\tilde{\bm{y}}_{t+h|t}=\psi\left(\hat{\bm{y}}_{t+h|t}\right)$ is said to ``reconcile'' a base forecast $\hat{\bm{y}}_{t+h|t}$ with respect to the mapping $\psi(.)$
	\end{definition}

	All reconciliation methods that we are aware of consider a linear mapping for $\psi$, which involves pre-multiplying base forecasts by an $n\times n$ matrix that has $\mathfrak{s}$ as its image.  One way to achieve this is with a matrix $\bm{SG}$, where $\bm{G}$ is an $(n-m)\times n$ matrix  (some authors use $\bm{P}$ used in place of $\bm{G}$).  This facilitates an interpretation of reconciliation as a two-step process, in the first step, base forecasts $\hat{\bm{y}}_{t+h|t}$ are combined to form a new set of bottom level forecasts, in the second step, these mapped to a full vector of coherent forecasts via pre-multiplication by $\bm{S}$.

	Although pre-multiplying base forecasts by $\bm{SG}$ will result in coherent forecasts, a number of desirable properties arise when $\bm{SG}$ has the specific structure of a {\em projection} matrix onto $\mathfrak{s}$.  In general a projection matrix is defined via the idemoptence property, i.e. $\bm{SG}^2=\bm{SG}$.  However a much more important property of projection matrices, used in multiple instances below, is that any vector lying in the image of the projection will be mapped to itself by that projection \citep[see Lemma 2.4 in][for a proof]{rao1974}. In our context this implies that for any $\bm{v}\in\mathfrak{s}$, $\bm{SGv}=\bm{v}$.

@@

	In this section we discuss two sensible properties that can be achieved by reconciliation via orthogonal projection.  The  first is that reconciliation should adjust the base forecasts as little as possible, i.e. the base and reconciled forecast should be `close'.  The second is that reconciliation in some sense should improve forecast accuracy, or more loosely, that the reconciled forecast should be `closer' to the realised value targeted by the forecast.

@@

	Consider the Euclidean distance between a forecast and the target. This is equivalent to the root of the sum of squared errors over the entire hierarchy. Let $\bm{y}_{t+h}$ be the realisation of the data generating process at time $t+h$. The following theorem shows that reconciliation never increases, and in most cases reduces, the sum of squared errors of point forecasts.

	\begin{theo}[Distance reducing property]\label{th:distred}
		If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal (in the Euclidean sense) projection onto $\mathfrak{s}$ and let $\|\bm{v}\|$ be the $L_2$ norm (in the Euclidean sense) of vector $\bm{v}$ then:
		\begin{equation}
		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|.
		\end{equation}
	\end{theo}
	\begin{proof}
		Since, $\bm{y}_{t+h},\tilde{\bm{y}}_{t+h}\in\mathfrak{s}$ and since the projection is orthogonal, by Pythagoras' theorem
		\begin{equation}
		\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2=\|(\tilde{\bm{y}}_{t+h|t}-\hat{\bm{y}}_{t+h})\|^2+\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2.
		\end{equation}

		Since $\|(\tilde{\bm{y}}_{t+h|t}-\hat{\bm{y}}_{t+h})\|^2\ge 0$ this implies,
		\begin{equation}
		\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2\ge\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2.
		\end{equation}
		with equality only holding when $\tilde{\bm{y}}_{t+h|t}=\hat{\bm{y}}_{t+h}$.  Taking the square root of both sides proves the desired result.
	\end{proof}

@@

	\begin{figure}[H]\label{fig:Schematic_OLSRecon}
		\centering
		\vspace{-0.9cm}
		\tiny
		\resizebox{\linewidth}{!}{\input{Figs/orth_pointforerec_schematic}}
		\caption{Orthogonal projection of $\hat{\bm{y}}$ onto $\mathfrak{s}$ yielding the reconciled forecast $\tilde{\bm{y}}$}

@@

    However, in other ways, Theorem~\ref{th:distred} is weaker than perhaps often understood. First, when improvements in forecast accuracy are discussed in the context of the theorem, this refers to a very specific measure of forecast accuracy.  In particular, this measure is the root of the sum of squared errors of {\em all} variables in the hierarchy.  As such, while forecast improvement is guaranteed for the hierarchy overall, reconciliation can lead to worse forecasts for individual series. Second, although orthogonal projections are guaranteed to improve on base forecasts, they are not necessarily the projection that leads to the greatest improvement in forecast accuracy.  As such referring to reconciliation via orthogonal projections as `optimal' is somewhat misleading since it does not have the optimality properties of some oblique projections, in particular MinT. It is to oblique projections that we now turn our attention.

@@

	One justification for using an orthogonal projection is that it leads to improved forecast accuracy in terms of the root of the sum of squared errors of {\em all} variables in the hierarchy.  A clear shortcoming of this measure of forecast accuracy is that forecasts errors in all series should not necessarily be treated equally.  For example, in hierarchies, top-level series tend to have a much larger scale than bottom level series.  Even when two series are on a similar scale, series that are more predictable or less variable will tend to be downweighted by simply aggregating square errors.  An even more sophisticated understanding may take the correlation between series into account.  All of these considerations lead towards reconciliation of the form $\tilde{\bm{y}}=\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}}$, where $\bm{W}$ is a symmetric matrix.  Generally, it is assumed that $\bm{W}$ is invertible, otherwise a pseudo inverse can be used.

	It should be noted that  $\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}$ is an oblique, rather than an orthogonal projection matrix in the usual Euclidean geometry.  However this matrix can be considered to be an orthogonal projection for a different geometry defined by the norm $||\bm{v}||_{{\bm W}^{-1}}=\bm{v}'\bm{W}^{-1}\bm{v}$, which we will call the generalised Euclidean geometry with respect to $\bm{W}^{-1}$.  One way to understand this geometry is that it is the same as Euclidean geometry when all vectors are first transformed by pre-multiplying by $\bm{W}^{-1/2}$.  This leads to a transformed $\bm{S}$ matrix $\bm{S}^*=\bm{W}^{-1/2}\bm{S}$ and transformed $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ vectors $\hat{\bm{y}}^*=\bm{W}^{-1/2}\hat{\bm{y}}$ and $\tilde{\bm{y}}^*=\bm{W}^{-1/2}\tilde{\bm{y}}$.  The transformed reconciled forecast results from an orthogonal projection in the transformed space since

	\begin{align}
	\tilde{\bm{y}}^*&=\bm{W}^{-1/2}\tilde{\bm{y}}\\&=\bm{W}^{-1/2}\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}}
	\\&=\bm{S}^*\left(\bm{S}^{*'}\bm{S}^*\right)^{-1}\bm{S}^{*'}\hat{\bm{y}^*}
	\end{align}

@@

	Note here that we rely here on the generalised Pythagorean Theorem (which involves an equality).  In contrast, \cite{WicEtAl2019} follow \cite{VanErven2015a} in stating their result in terms of the Generalised Pythagorean Inequality.  The proof of \cite{WicEtAl2019} requires an assumptions about convexity so that the angle between the base forecast and coherent subspace must be greater than 90 degrees.  The proof we have provided here requires no such assumption, since this may not hold for an arbitrary $\bm{W}$.  As such the statement from \cite{WicEtAl2019} that {\em``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified; this is only true in with respect to a loss function that depends on ${\bm W}$.  If Euclidean distance (or mean squared error) is used, there will be cases where the MinT estimator does not improve upon base forecasts.

@@

	Figure~\ref{fig:MinT_justification1} provides geometrical intuition into the MinT method.  Suppose the in-sample errors are given by the orange points.  They provide information on the most likely direction of large deviations from the coherent subspace.  This direction is denoted by $\bm{R}$.  Figure~\ref{fig:MinT_justification2} then shows a target value of $\bm{y}$, while the grey points indicate possible values for the base forecasts (the base forecasts are of course stochastic).  One possible value of the forecast is depicted in blue as $\hat{\bm{y}}$.  An oblique projection of the blue point back along the direction of $\bm{R}$ yields a reconciled forecast closer to the target, especially compared to an orthogonal projection showed as in Figure \ref{fig:Orthogonal_projection_all_points}.  Figure \ref{fig:Oblique_projection_all_points} depicts a similar oblique projection along $\bm{R}$ for all the gray points yield reconciled forecasts tightly packed near the target $\bm{y}$.  In this sense, the oblique MinT projection minimises the forecast error variance of reconciled forecasts. In contrast to the result in Theorem~\ref{th:gdistred}, this property is a statistical property in the sense that MinT is optimal in expectation.

@@

	The property that projections map all vectors in the coherent subspace onto themselves is also useful in proving the unbiasedness preserving property of reconciliation \cite{WicEtAl2019}.  Before restating this proof using a  clear geometric interpretation we discuss in a precise fashion what is meant by unbiasedness.

>>>>

	\if1\blind
	{
		\title{\bf Forecasts Reconciliation: A geometric view with new insights on bias correction.}
		\author{Anastasios Panagiotelis\thanks{
				The authors gratefully acknowledge the support of Australian Research Council Grant DP140103220.  We also thank Professor Mervyn Silvapulle for valuable comments.}\hspace{.2cm}\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3145, Australia.\\
			Email: Anastasios.Panagiotelis@monash.edu \\
			and \\
			Puwasala Gamakumara\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3800, Australia.\\
			Email: Puwasala.Gamakumara@monash.edu \\
			and \\
			George Athanasopoulos\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3145, Australia.\\
			Email: George.Athanasopoulos@monash.edu \\
			and \\
			Rob J Hyndman\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3800, Australia.\\
			Email: Rob.Hyndman@monash.edu \\}
		\maketitle
	} \fi

@@

	Multivariate time series following an aggregation structure arise in many disciplines such as manufacturing, engineering, marketing and medicine\todo{include references}. Forecasts of these series should adhere to aggregation constraints to ensure aligned decision making. Earlier studies achieved this by only forecasting a single level of the hierarchy and then either aggregating in a bottom-up fashion \citep{Dunn1976} or disaggregating in a top-down fashion \citep{Gross1990, Athanasopoulos2009}.  For reviews of these approaches including a discussion of their advantages and disadvantages see \citet{Schwarzkopf1988, Kahn1998, Lapide1998, Fliedner2001}.

	In contrast to these methods, \cite{Hyndman2011} proposed forecasting all series in the hierarchy, referring to these as {\em base} forecasts.  Since base forecasts were produced independently they were not guaranteed to adhere to aggregation constraints and could thus be improved via further adjustment.  A framework was proposed whereby the base forecasts were assumed to follow a regression model.  The predicted values from this model were guaranteed to adhere to the linear constraints by construction and could thus be used as a new set of forecasts.  This approach and later modifications have subsequently been shown to outperform bottom-up and top-down approaches in a variety of empirical settings\todo{references}.

@@

	The remainder of this paper is structured as follows. Section~\ref{sec:CoheForecasts} deals with the concept of coherence and defines so called hierarchical time series in a way that does not depend on any notion of bottom-level series.  Section~\ref{sec:Reconciliation} defines forecast reconciliation in terms of projections and includes a proof that reconciled forecasts dominate base forecasts with respect to a specific loss function. In Section~\ref{sec:BiasInRecon} we prove the unbiasedness preserving property of reconciliation via certain projection matrices and propose methods for bias correction. In Section \ref{sec:EmpStudy} we evaluate these methods for in an extensive emprirical application to domestic tourism flow in Australia.  Section~\ref{sec:conclusions} concludes with some discussion and thoughts on the  future of research in forecast reconciliation.
\section{Coherent forecasts}\label{sec:CoheForecasts}

@@

    We briefly define the concept of a \emph{hierarchical time series} in a fashion similar to \cite{AthEtAl2019_MacroBook}, \cite{FPP2018} and others, before elaborating on some of the limitations of this understanding.  A \emph{hierarchical time series} is a collection of $n$ variables indexed by time, where some variables are aggregates of other variables. We let $\bm{y}_t \in \mathbb{R}^n$ be a vector comprising observations of all variables in the hierarchy at time $t$. The \emph{bottom-level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables; we let $\bm{b}_t \in \mathbb{R}^m$ be a vector comprised of observations of all bottom-level series at time $t$.  The hierarchical structure of the data implies that the following holds for all $t$

@@

     To further illustrate, Figure \ref{fig:3D_hierarchy} depicts the most simple three variable hierarchy where $y_{Tot,t}=y_{A,t}+y_{B,t}$.  The coherent subspace is depicted as a grey $2$-dimensional plane within $3$-dimensional space, i.e. $m=2$ and $n=3$.  It is worth noting that the coherent subspace is spanned by the columns of $\bm{S}$, i.e.\ $\mathfrak{s}=\text{span}(\bm{S})$.  In Figure~\ref{fig:3D_hierarchy}, these columns are $\vec{s}_1=(1,1,0)'$ and $\vec{s}_2=(1,0,1)'$.  However, it is equally important to recognise that the hierarchy could also have been defined in terms of $y_{Tot,t}$ and $y_{A,t}$ rather than the bottom-level series, $y_{A,t}$ and $y_{B,t}$. In this case the corresponding `$\bm{S}$ matrix' would have columns $(1,0,1)'$ and $(0,1,-1)'$.  However, while there are multiple ways to define an $\bm{S}$ matrix, in all cases the columns will span the same coherent subspace, which is unique.

     \begin{figure}[H]
     	\centering
     	\vspace{-0.9cm}
     	\small
     	\resizebox{\linewidth}{!}{
     		\input{Figs/3D_hierarchy}
     	}
     	\caption{Depiction of a three dimensional hierarchy with $y_{\text{Tot}} = y_{\text{A}} + y_{\text{B}}$. The gray coloured two dimensional plane depicts the coherent subspace $\mathfrak{s}$ where $\vec{s}_1 = (1,1,0)'$ and $\vec{s}_2 = (1, 0, 1)'$ are basis vectors that span $\mathfrak{s}$. The red points in $\mathfrak{s}$ represent realisations or coherent forecasts}\label{fig:3D_hierarchy}
     \end{figure}

@@

	 Despite the common use of the term {\em hierarchical time series}, it should be clear from the definition that the data need not necessarily follow a hierarchy.  Also notable by its absence in the above definition is any reference to {\em aggregation}. In some ways, terms such as {\em hierarchical} and {\em aggregation} can be misleading since the literature has covered instances that cannot be depicted in a similar fashion to Figure~\ref{fig:basichier} and/or do not involve aggregation. Examples include, temporal hierarchies which involve grouped structures \citep[see][]{AthEtAl2017}, overlapping temporal hierarchies \citep[see][]{JeoEtAl2019}, applications for which the difference rather than the aggregate is of interest \cite[see][]{LiTan2019}, or structures that involve both cross-sectional and temporal dimensions referred to as cross-temporal structures \citep[see][]{KouAth2019}. Finally, although Definition~\ref{def:cohspace} makes reference to time series, this definition can be easily generalised to any vector-valued data for which some linear constraints are known to hold for all realisations.

@@

    Without any loss of generality, the above definition could also be applied to prediction for multivariate data in general, rather than just forecasting of time series.

    Much of the early literature that dealt with the problem of forecasting hierarchical time series \citep[see][and references therein]{Gross1990} produced forecasts at a single level of the hierarchy in the first stage. Subsequently forecasts for all series were recovered through aggregation, disaggregation according to historical or forecast proportions or some combination of both.  As such incoherent forecasts were not a problem in these earlier papers.

    Forecasting a single level of the hierarchy did not, however echo common practice within many industries.\todo{might need refs}  In many organisations different departments or `silos' each produced their own forecasts, often with their own information sets and judgemental adjustments.  This approach does have several advantages over only forecasting a single level.  First, there is no loss of information since all levels and series are modelled.  Second, modelling higher level series often identifies features such as trend and seasonality that cannot be detected in noisy disaggregate data.  However, when forecasts are produced independently at all levels, forecasts are likely to be incoherent.\footnote{There are some special cases of using simple approaches such as na\"{i}ve, which extrapolate the coherent nature of the data to the forecasts.} This problem of incoherent forecasts cannot in general be solved by multivariate modelling either.  Instead, the solution is to make an ex post adjustment that ensures coherence, a process known as {\em forecast reconciliation}

@@

	The concept of forecast reconciliation is predicated on there being an $n$-vector of forecasts that are incoherent.  We call these {\em base forecasts} and denote them as $\hat{\bm{y}}_{t+h|t}$. The subscript $t+h/t$ implies that the forecast is made at time $t$ for a period $h$ steps into the future.  In the sequel, this subscript will be dropped at times for ease of exposition.  In the most general terms, reconciliation can be defined as follows.

	\begin{definition}[Reconciled forecasts]\label{def:reconpoint}
		Let $\psi$ be a mapping, $\psi:\mathbb{R}^n\rightarrow\mathfrak{s}$.  The point forecast $\tilde{\bm{y}}_{t+h|t}=\psi\left(\hat{\bm{y}}_{t+h|t}\right)$ ``reconciles'' a base forecast $\hat{\bm{y}}_{t+h|t}$ with respect to the mapping $\psi(.)$
	\end{definition}

	All reconciliation methods that we are aware of consider a linear mapping for $\psi$, which involves pre-multiplying base forecasts by an $n\times n$ matrix that has $\mathfrak{s}$ as its image.  One way to achieve this is with a matrix $\bm{SG}$, where $\bm{G}$ is an $m\times n$ matrix  (some authors use $\bm{P}$ in place of $\bm{G}$).  This facilitates an interpretation of reconciliation as a two-step process. In the first step, base forecasts $\hat{\bm{y}}_{t+h|t}$ are combined to form a new set of bottom-level forecasts. In the second step, these are mapped to a full vector of coherent forecasts via pre-multiplication by $\bm{S}$.

	Although pre-multiplying base forecasts by $\bm{SG}$ will result in coherent forecasts, a number of desirable properties arise when $\bm{SG}$ has the specific structure of a {\em projection} matrix onto $\mathfrak{s}$.  In general a projection matrix is defined via its idempotence property, i.e. $(\bm{SG})^2=\bm{SG}$.  However a much more important property of projection matrices, used in multiple instances below, is that any vector lying in the image of the projection will be mapped to itself by that projection \citep[see Lemma 2.4 in][for a proof]{rao1974}. In our context this implies that for any $\bm{v}\in\mathfrak{s}$, $\bm{SGv}=\bm{v}$.

@@

	In this section we discuss two sensible properties that can be achieved by reconciliation via orthogonal projection.  
\begin{itemize}
  \item The  first is that reconciliation should adjust the base forecasts as little as possible, i.e. the base and reconciled forecasts should be `close'. 
  \item The second is that reconciliation in some sense should improve forecast accuracy, or more loosely, that the reconciled forecast should be `closer' to the realised value targeted by the forecast.
\end{itemize}

@@

	Consider the Euclidean distance between a forecast and the target. This is equivalent to the root of the sum of squared forecast errors over the entire hierarchy. Let $\bm{y}_{t+h}$ be the realisation of the data generating process at time $t+h$. The following theorem shows that reconciliation never increases, and in most cases reduces, the sum of squared errors of point forecasts.

	\begin{theo}[Distance reducing property]\label{th:distred}
		If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal (in the Euclidean sense) projection onto $\mathfrak{s}$ and let $\|\bm{v}\|$ be the $L_2$ norm (in the Euclidean sense) of vector $\bm{v}$ then:
		\begin{equation}
		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|.
		\end{equation}
	\end{theo}
	\begin{proof}
		Since, $\bm{y}_{t+h|t},\tilde{\bm{y}}_{t+h|t}\in\mathfrak{s}$ and since the projection is orthogonal, by Pythagoras' theorem
		\begin{equation}
		\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2=\|(\tilde{\bm{y}}_{t+h|t}-\hat{\bm{y}}_{t+h|t})\|^2+\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2.
		\end{equation}

		Since $\|(\tilde{\bm{y}}_{t+h|t}-\hat{\bm{y}}_{t+h|t})\|^2\ge 0$ this implies,
		\begin{equation}
		\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2\ge\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2.
		\end{equation}
		with equality only holding when $\tilde{\bm{y}}_{t+h|t}=\hat{\bm{y}}_{t+h|t}$.  Taking the square root of both sides proves the desired result.
	\end{proof}

@@

	\begin{figure}[H]
		\centering
		\vspace{-0.9cm}
		\tiny
		\resizebox{\linewidth}{!}{\input{Figs/orth_pointforerec_schematic}}
		\caption{Orthogonal projection of $\hat{\bm{y}}$ onto $\mathfrak{s}$ yielding the reconciled forecast $\tilde{\bm{y}}$}\label{fig:Schematic_OLSRecon}

@@

    However, in other ways, Theorem~\ref{th:distred} is weaker than perhaps often understood. First, when improvements in forecast accuracy are discussed in the context of the theorem, this refers to a very specific measure of forecast accuracy.  In particular, this measure is the root of the sum of squared forecast errors of {\em all} variables in the hierarchy.  As such, while forecast improvement is guaranteed for the hierarchy overall, reconciliation can lead to less accurate forecasts for individual series. Second, although orthogonal projections are guaranteed to improve on base forecasts, they are not necessarily the projection that leads to the greatest improvement in forecast accuracy.  As such referring to reconciliation via orthogonal projections as `optimal' is somewhat misleading since it does not have the optimality properties of some oblique projections, in particular MinT. It is to oblique projections that we now turn our attention.

@@

	One justification for using an orthogonal projection is that it leads to improved forecast accuracy in terms of the root of the sum of squared errors of {\em all} variables in the hierarchy.  A clear shortcoming of this measure of forecast accuracy is that forecast errors in all series should not necessarily be treated equally.  For example, in hierarchies, top-level series tend to have a much larger scale than bottom-level series.  Even when two series are on a similar scale, series that are more predictable or less variable will tend to be downweighted by simply aggregating squared errors.  An even more sophisticated understanding may take the correlation between series into account.  All of these considerations lead towards reconciliation of the form $\tilde{\bm{y}}=\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}}$, where $\bm{W}$ is a symmetric matrix.  Generally, it is assumed that $\bm{W}$ is invertible, otherwise a pseudo inverse can be used.

	It should be noted that  $\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}$ is an oblique, rather than an orthogonal projection matrix in the usual Euclidean geometry.  However this matrix can be considered to be an orthogonal projection for a different geometry defined by the norm\break $||\bm{v}||_{{\bm W}^{-1}}=\bm{v}'\bm{W}^{-1}\bm{v}$, referred to as the generalised Euclidean geometry with respect to $\bm{W}^{-1}$.  One way to understand this geometry is that it is the same as Euclidean geometry when all vectors are first transformed by pre-multiplying by $\bm{W}^{-1/2}$.  This leads to a transformed $\bm{S}$ matrix $\bm{S}^*=\bm{W}^{-1/2}\bm{S}$ and transformed $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ vectors $\hat{\bm{y}}^*=\bm{W}^{-1/2}\hat{\bm{y}}$ and $\tilde{\bm{y}}^*=\bm{W}^{-1/2}\tilde{\bm{y}}$.  The transformed reconciled forecast results from an orthogonal projection in the transformed space since

	\begin{align}
	\tilde{\bm{y}}^*&=\bm{W}^{-1/2}\tilde{\bm{y}}\\&=\bm{W}^{-1/2}\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}}
	\\&=\bm{S}^*\left(\bm{S}^{*'}\bm{S}^*\right)^{-1}\bm{S}^{*'}\hat{\bm{y}^*}.
	\end{align}

@@

	\todo{Rob can you please read to make sure you are happy with this.}Note here that we rely here on the generalised Pythagorean Theorem (which involves an equality).  In contrast, \cite{WicEtAl2019} follow \cite{VanErven2015a} in stating their result in terms of the Generalised Pythagorean Inequality.  The proof of \cite{WicEtAl2019} requires an assumption about convexity so that the angle between the base forecast and coherent subspace must be greater than 90 degrees.  The proof we have provided here requires no such assumption, since this may not hold for an arbitrary $\bm{W}$.  As such the statement from \cite{WicEtAl2019} that {\em``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified; this is only true in with respect to a loss function that depends on ${\bm W}$.  If Euclidean distance (or mean squared error) is used, there will be cases where the MinT estimator does not improve upon base forecasts.

@@

	Figure~\ref{fig:MinT_justification1} provides geometrical intuition into the MinT method.  Suppose the in-sample errors are given by the orange points.  They provide information on the most likely direction of large deviations from the coherent subspace.  This direction is denoted by $\bm{R}$.  Figure~\ref{fig:MinT_justification2} then shows a target value of $\bm{y}$, while the grey points indicate possible values for the base forecasts (the base forecasts are of course stochastic).  One possible value of the forecast is depicted in blue as $\hat{\bm{y}}$.  An oblique projection of the blue point back along the direction of $\bm{R}$ yields a reconciled forecast closer to the target, especially compared to an orthogonal projection shown in Figure \ref{fig:Orthogonal_projection_all_points}.  Figure \ref{fig:Oblique_projection_all_points} depicts an oblique projection along $\bm{R}$ for all the gray points, yielding reconciled forecasts tightly packed near the target $\bm{y}$.  In this sense, the oblique MinT projection minimises the forecast error variance of the reconciled forecasts. In contrast to the result in Theorem~\ref{th:gdistred}, this property is a statistical property in the sense that MinT is optimal in expectation.

@@

	The property that projections map all vectors in the coherent subspace onto themselves is also useful in proving the unbiasedness preserving property of reconciliation of \cite{WicEtAl2019}.  Before restating this proof using a  clear geometric interpretation we discuss in a precise fashion what is meant by unbiasedness.
